Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-03-23 paper/zhang-cook-laa-langrene-menendez.Rmd
Final few changes.

- \code{get\_*()} extracts and manipulates certain components from the existing data object.
  - \code{get\_anchor()} extracts target observations 
  - \code{get\_basis\_matrix()} flattens all the bases into a matrix
  - \code{get\_best()} extracts the observation with the highest index value in the data object
  - \code{get\_dir\_search()} extracts directional search observations for PD search
  - \code{get\_interp()} extracts interpolated observations
  - \code{get\_interp\_last()} extracts the ending interpolated observations in each iteration
  - \code{get\_interrupt()} extracts the ending interpolated observations and the target observations if  the interpolation is interrupted
  - \code{get\_search()} extracts search observations 
  - \code{get\_search\_count()} extracts the count of search observations 
  - \code{get\_space\_param()} produces the coordinates of the centre and radius of the basis space
  - \code{get\_start()} extracts the starting observation
  - \code{get\_theo()} extracts the theoretical best observations, if presented

@@

- \code{add\_*()} create ggprotos for different components for the PCA plot
  - \code{add\_anchor()} is a wrapper for plotting anchor bases
  - \code{add\_anno()} is a wrapper for annotating the symmetry of start bases
  - \code{add\_dir\_search()} is a wrapper for plotting the directional search bases with magnified distance
  - \code{add\_end()} is a wrapper for plotting end bases
  - \code{add\_interp()} is a wrapper for plotting the interpolation path
  - \code{add\_interp\_last()} is a wrapper for plotting the last interpolation bases for comparing with target bases when interruption is carried
  - \code{add\_interrupt()} is a wrapper for linking the last interpolation bases with target ones when interruption is carried
  - \code{add\_search()} is a wrapper for plotting search bases
  - \code{add\_space()} is a wrapper for plotting the circular space 
  - \code{add\_start()} is a wrapper for plotting start bases
  - \code{add\_theo()} is a wrapper for plotting theoretical best bases, if applicable

@@

This paper has illustrated setting up a data object that can be used for diagnosing a complex optimisation procedure. The ideas were illustrated using the optimisers available for projection pursuit guided tour. Here the constraint is the orthonormality condition of the projection bases. The approach used here could be broadly applied to understand other constrained optimisers.

<!-- something about the diagnostic plots  -->
Four diagnostic plots have been introduced to investigate the progression and the projection space of an optimiser. The implementation of these visualisations is designed to be easy-to-use with each plot can be produced with a simple supply of the data object. More advanced users may decide to modify on top of the basic plots or even build their own.

>>>>

- \code{get\_*()} extracts and manipulates certain components from the existing data object.
  - \code{get\_anchor()} extracts target observations 
  - \code{get\_basis\_matrix()} flattens all the bases into a matrix
  - \code{get\_best()} extracts the observation with the highest index value in the data object
  - \code{get\_dir\_search()} extracts directional search observations for PD search
  - \code{get\_interp()} extracts interpolated observations
  - \code{get\_interp\_last()} extracts the ending interpolated observations in each iteration
  - \code{get\_interrupt()} extracts the ending interpolated observations and the target observations if  the interpolation is interrupted
  - \code{get\_search()} extracts search observations 
  - \code{get\_search\_count()} extracts the count of search observations 
  - \code{get\_space\_param()} produces the coordinates of the centre and radius of the basis space
  - \code{get\_start()} extracts the starting observation
  - \code{get\_theo()} extracts the theoretical best observations, if given

@@

- \code{add\_*()} provides wrapper functions to create ggprotos for different components for the PCA plot
  - \code{add\_anchor()} for plotting anchor bases
  - \code{add\_anno()} for annotating the symmetry of start bases
  - \code{add\_dir\_search()} for plotting the directional search bases with magnified distance
  - \code{add\_end()} for plotting end bases
  - \code{add\_interp()} for plotting the interpolation path
  - \code{add\_interp\_last()} for plotting the last interpolation bases for comparing with target bases when interruption is used
  - \code{add\_interrupt()} for linking the last interpolation bases with target ones when interruption is used
  - \code{add\_search()} for plotting search bases
  - \code{add\_space()} for plotting the circular space 
  - \code{add\_start()} for plotting start bases
  - \code{add\_theo()} for plotting theoretical best bases, if applicable

@@

This paper has set up a data object that can be used for diagnosing a complex optimisation procedure. The ideas were illustrated using the optimisers available for projection pursuit guided tour. Here the constraint is the orthonormality condition of the projection bases. The approach used broadly applies to other constrained optimisers.

<!-- something about the diagnostic plots  -->
Four diagnostic plots have been introduced to investigate the progression of the optimiser and the coverage in search space. The implementation of these visualisations is designed to be easy-to-use, each plot can be produced by supplying the data object to the corresponding function. More advanced users may decide to modify these basic graphs using the provided wrapper functions, or even build their own.

### 2021-03-23 paper/zhang-cook-laa-langrene-menendez.tex
Final few changes.

  \begin{itemize}
  \tightlist
  \item
    \code{get\_anchor()} extracts target observations
  \item
    \code{get\_basis\_matrix()} flattens all the bases into a matrix
  \item
    \code{get\_best()} extracts the observation with the highest index
    value in the data object
  \item
    \code{get\_dir\_search()} extracts directional search observations
    for PD search
  \item
    \code{get\_interp()} extracts interpolated observations
  \item
    \code{get\_interp\_last()} extracts the ending interpolated
    observations in each iteration
  \item
    \code{get\_interrupt()} extracts the ending interpolated
    observations and the target observations if the interpolation is
    interrupted
  \item
    \code{get\_search()} extracts search observations
  \item
    \code{get\_search\_count()} extracts the count of search
    observations
  \item
    \code{get\_space\_param()} produces the coordinates of the centre
    and radius of the basis space
  \item
    \code{get\_start()} extracts the starting observation
  \item
    \code{get\_theo()} extracts the theoretical best observations, if
    presented
  \end{itemize}
\item
  \code{bind\_*()} incorporates additional information outside the tour
  optimisation into the data object.

  \begin{itemize}
  \tightlist
  \item
    \code{bind\_theoretical()} binds the theoretical best observation in
    simulated experiment
  \item
    \code{bind\_random()} binds randomly generated bases in the
    projection bases space to the data object
  \item
    \code{bind\_random\_matrix()} binds randomly generated bases and
    outputs in a matrix format
  \end{itemize}
\item
  \code{add\_*()} create ggprotos for different components for the PCA
  plot

  \begin{itemize}
  \tightlist
  \item
    \code{add\_anchor()} is a wrapper for plotting anchor bases
  \item
    \code{add\_anno()} is a wrapper for annotating the symmetry of start
    bases
  \item
    \code{add\_dir\_search()} is a wrapper for plotting the directional
    search bases with magnified distance
  \item
    \code{add\_end()} is a wrapper for plotting end bases
  \item
    \code{add\_interp()} is a wrapper for plotting the interpolation
    path
  \item
    \code{add\_interp\_last()} is a wrapper for plotting the last
    interpolation bases for comparing with target bases when
    interruption is carried
  \item
    \code{add\_interrupt()} is a wrapper for linking the last
    interpolation bases with target ones when interruption is carried
  \item
    \code{add\_search()} is a wrapper for plotting search bases
  \item
    \code{add\_space()} is a wrapper for plotting the circular space
  \item
    \code{add\_start()} is a wrapper for plotting start bases
  \item
    \code{add\_theo()} is a wrapper for plotting theoretical best bases,
    if applicable
  \end{itemize}
\item
  Utilities

@@

This paper has illustrated setting up a data object that can be used for
diagnosing a complex optimisation procedure. The ideas were illustrated
using the optimisers available for projection pursuit guided tour. Here
the constraint is the orthonormality condition of the projection bases.
The approach used here could be broadly applied to understand other
constrained optimisers.

Four diagnostic plots have been introduced to investigate the
progression and the projection space of an optimiser. The implementation
of these visualisations is designed to be easy-to-use with each plot can
be produced with a simple supply of the data object. More advanced users
may decide to modify on top of the basic plots or even build their own.

>>>>

  \begin{itemize}
  \tightlist
  \item
    \code{get\_anchor()} extracts target observations
  \item
    \code{get\_basis\_matrix()} flattens all the bases into a matrix
  \item
    \code{get\_best()} extracts the observation with the highest index
    value in the data object
  \item
    \code{get\_dir\_search()} extracts directional search observations
    for PD search
  \item
    \code{get\_interp()} extracts interpolated observations
  \item
    \code{get\_interp\_last()} extracts the ending interpolated
    observations in each iteration
  \item
    \code{get\_interrupt()} extracts the ending interpolated
    observations and the target observations if the interpolation is
    interrupted
  \item
    \code{get\_search()} extracts search observations
  \item
    \code{get\_search\_count()} extracts the count of search
    observations
  \item
    \code{get\_space\_param()} produces the coordinates of the centre
    and radius of the basis space
  \item
    \code{get\_start()} extracts the starting observation
  \item
    \code{get\_theo()} extracts the theoretical best observations, if
    given
  \end{itemize}
\item
  \code{bind\_*()} incorporates additional information outside the tour
  optimisation into the data object.

  \begin{itemize}
  \tightlist
  \item
    \code{bind\_theoretical()} binds the theoretical best observation in
    simulated experiment
  \item
    \code{bind\_random()} binds randomly generated bases in the
    projection bases space to the data object
  \item
    \code{bind\_random\_matrix()} binds randomly generated bases and
    outputs in a matrix format
  \end{itemize}
\item
  \code{add\_*()} provides wrapper functions to create ggprotos for
  different components for the PCA plot

  \begin{itemize}
  \tightlist
  \item
    \code{add\_anchor()} for plotting anchor bases
  \item
    \code{add\_anno()} for annotating the symmetry of start bases
  \item
    \code{add\_dir\_search()} for plotting the directional search bases
    with magnified distance
  \item
    \code{add\_end()} for plotting end bases
  \item
    \code{add\_interp()} for plotting the interpolation path
  \item
    \code{add\_interp\_last()} for plotting the last interpolation bases
    for comparing with target bases when interruption is used
  \item
    \code{add\_interrupt()} for linking the last interpolation bases
    with target ones when interruption is used
  \item
    \code{add\_search()} for plotting search bases
  \item
    \code{add\_space()} for plotting the circular space
  \item
    \code{add\_start()} for plotting start bases
  \item
    \code{add\_theo()} for plotting theoretical best bases, if
    applicable
  \end{itemize}
\item
  Utilities

@@

This paper has set up a data object that can be used for diagnosing a
complex optimisation procedure. The ideas were illustrated using the
optimisers available for projection pursuit guided tour. Here the
constraint is the orthonormality condition of the projection bases. The
approach used broadly applies to other constrained optimisers.

Four diagnostic plots have been introduced to investigate the
progression of the optimiser and the coverage in search space. The
implementation of these visualisations is designed to be easy-to-use,
each plot can be produced by supplying the data object to the
corresponding function. More advanced users may decide to modify these
basic graphs using the provided wrapper functions, or even build their
own.
